Appendix S1

### 2020-04-21 manuscript/appendix.Rmd
link to code supplement
fix carlson ref

```{r 02_cdl_key, results='asis', warning=FALSE, echo = FALSE}
knitr::kable('', col.names = NULL, caption = "Category definitions from the 2010 CDL. See code supplement for listing of variables classified as 'ag'.")
```

@@

```{r trophic_state, fig.cap="Lake trophic state in our study lakes versus all lakes from Soranno et al. (2017) located within our study extent. Trophic state based on the chlorophyll critera from Carlson (1996).", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}

>>>>

```{r 02_cdl_key, results='asis', warning=FALSE, echo = FALSE}
knitr::kable('', col.names = NULL, caption = "Category definitions from the 2010 CDL. See code supplement for listing of variables classified as 'ag' (https://doi.org/10.5281/zenodo.3754916).")
```

@@

```{r trophic_state, fig.cap="Lake trophic state in our study lakes versus all lakes from Soranno et al. (2017) located within our study extent. Trophic state based on the chlorophyll criteria from Carlson and Simpson (1996).", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}
